### 2024-09-11 article_codes.qmd
Add table with number of wilfires by building density breaks

## Effect distance to large forest

@@

## Effect threshold building density

>>>>

## Wilfires and building density

Calculate the building density of the grid of 250 x 250 m where the wilfire originated.

```{r}
#| label: fig-wilfires-number-buildings
#| fig-cap: Number of buildings per grid cells of 250 m x 250 m and wildfires (red points)

ggplot() +
  tidyterra::geom_spatvector(data = region_v, fill = "white") +
  tidyterra::geom_spatraster(data = build_focal) +
  scale_fill_whitebox_c(name = "N. Buildings",
                        palette = "viridi",
                        trans = "log10") +
  geom_sf(data = wf, col = "red", size = 1) +
  theme_void()

```{r}
#| label: fig-wildfires-buildings-density
#| fig-cap: Histogram of building density in each wildfire

# Link wildfires with building density (build_focal) 
wf_build_density <- extract(build_focal, wf) |>
  # Assign 0 to NAs --> No buildings
  mutate(focal_sum = ifelse(is.na(focal_sum), 0, focal_sum)) |> 
  # Building density is the number of buildings / buffer area 
  # buffer area = circular moving window of 500 m
  mutate(bd = focal_sum / area_buffer)

ggplot(wf_build_density, aes(x = bd)) + 
  geom_histogram(bins = 50, color = "darkblue", fill = "lightblue") + 
  theme_bw()
```

```{r}
#| label: tbl-wildfires-buildings-density
#| tbl-cap: Number of wildfires

brks <-  c(0,  1, 3, 6, 10, 20, 50, 100, 500, 1700)
wf_build_density |> 
  mutate(bd_brks = cut(bd, 
                       brks,
                       include.lowest = TRUE,
                       right = FALSE,
                       dig.lab = 4)) |> 
  group_by(bd_brks) |> 
  summarise(n = n(), 
            perc = n() / nrow(wf_build_density) * 100) |> 
  mutate(cs = cumsum(perc)) |> 
  gt() |> 
  fmt_number(columns = c("perc", "cs"),
             decimals = 1) |> 
  tab_spanner(label = md("**Wildfires**"),
              columns = c(n, perc, cs)) |> 
  cols_label(
    bd_brks = md(html("**Building**<br>**density**")),
    n  = md("**Number**"),
    perc = md("**Percentage [%]**"),
    cs = md("**Cumulative [%]**")
  )

## WUI definition

@@
